%------------------------------------
% Sherry Yong Chen
% Typesetting your academic CV in LaTeX
%
% URL: https://sherrychen.org
% DISCLAIMER: This template is provided for free and without any guarantee
% that it will correctly compile on your system if you have a non-standard
% configuration.
% Some rights reserved: http://creativecommons.org/licenses/by-sa/3.0/
%------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11.5pt, a4paper]{article}
\usepackage{fontspec}

% DOCUMENT LAYOUT
\usepackage{geometry}
\geometry{a4paper, textwidth=5.5in, textheight=9in, marginparsep=5pt, marginparwidth=.6in}
\setlength\parindent{0in}

% FONTS
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
\usepackage[super]{nth}

%\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O}
%\setmonofont[Scale=0.8]{Monaco}

\setmainfont[
  Ligatures={Common}, Numbers={OldStyle}, Variant={01},
  BoldFont={LinLibertine_RB.otf},
  ItalicFont={LinLibertine_RI.otf},
  BoldItalicFont={LinLibertine_RBI.otf}
]{LinLibertine_R.otf}
\setmonofont[Scale=0.8]{DejaVuSansMono.ttf}

% ---- CUSTOM COMMANDS
\chardef\&="E050
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\newcommand{\doi}[1]{\href{#1}{\scriptsize\textsc{[doi]}}}
% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\amper{}}{\chardef\amper="E0BD }
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\reversemarginpar

% HEADINGS
\usepackage{sectsty}
\usepackage[normalem]{ulem}
\sectionfont{\mdseries\upshape\Large}
\subsectionfont{\mdseries\scshape\normalsize}
\subsubsectionfont{\mdseries\upshape\large}


% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[%dvipdfm,
bookmarks, colorlinks, breaklinks,
% ---- FILL IN HERE THE TITLE AND AUTHOR
	pdftitle={UtkuTurk-CV},
	pdfauthor={Utku Turk},
	pdfproducer={http://nitens.org/taraborelli/cvtex}
]{hyperref}
\hypersetup{linkcolor=black,citecolor=black,filecolor=black,urlcolor=black}

%SYMBOLS
\usepackage[misc]{ifsym}
\usepackage{marvosym}
\usepackage{url}
\usepackage{fontspec}
\usepackage{fontawesome}
%\newfontfamily{\FA}{fontawesome.otf}


% DOCUMENT
\begin{document}
{\Huge Utku Türk}\\[1cm]
Boğaziçi Unv. JF Building \# 314 Be\c{s}ikta\c{s}, \.{I}stanbul 34342 \\ 
Turkey \\[.2cm]
\Letter{ utku.turk@boun.edu.tr} \\
\Mundus~\url{ http://utkuturk.com} \\
\faGithub \thinspace \href{https://github.com/utkuturk}{\thinspace utkuturk}
\faTwitter \href{link}{\thinspace theutkuturk} \\

%%\hrule
\section*{\faLightbulbO \thinspace Areas of interest}

\years{Broad} Formal Semantics, Psycholinguistics, Nanosyntax \\
\years{Narrow} Conditionals, Adjectival Morphology, Case Theory, Memory Retrieval in Sentence Processing \\

%\hrule
\section*{\faGraduationCap \thinspace Education}

\subsection*{Degree seeking programs}
\noinden

\years{2017-Present}\textbf{M.A in Linguistics}, Boğaziçi University  \\

\years{2012-2017}\textbf{B.A in Translation Studies}, Boğaziçi University  \\

 %\hrule
 \subsection*{Non-degree studies}
 \noindent
 \years{2019 Summer}DGfs Summer School - XPrag.de: New Pragmatic Theories based on Experimental Evidence \\
 \years{2015-2016}Exchange student in UCLA, the Department of Linguistics

%\hrule
\section*{\faBriefcase \thinspace Work Experience}

\years{2018-Present}Graduate Research Assistant in the Department of Linguistics, \textsc{Boğaziçi University} \\
  • write up administrative stuff \\
  • write about taing \\
  • write about helping for research and foreign faculty members in their stuff with turkey \\
  
\years{2018 Summer}Turkish Language Instructor in the Turkish Language and Culture Program, \textsc{Boğaziçi University}\\
  • write up administrative stuff \\



%\hrule
\section*{\faUniversity \thinspace Research experiences}

\years{2015-2017}Research Assistant in A Very Nice Lab, \textsc{University of Blah} \\
  • PI: Dr Blah Blah \\
  • Projects: Blah Blah Blah \\


%\hrule
\section*{\faBook \thinspace Publications}

\subsection*{Book chapters}
\noindent
\years{2017}\textbf{Name.} Title. Book.

\subsection*{Articles}
\noindent
\years{2017}\textbf{Name.} Title. Jounral. \\

%\hrule
\section*{\faEdit \thinspace Manuscripts}

\subsection*{Work in progress}
\noindent
\years{2017}\textbf{Name.} Title.

\subsection*{Thesis \& Research papers}
\noindent
\years{2017}\textbf{Name.} Title. \\


%\hrule
\section*{\faMicrophone \thinspace Posters \& Presentations}

\subsection*{Oral presentations}
\noindent
\years{2017}\textbf{Name.} Title. Presentation given at Blah Conference, Date \& Year, Univeristy of Blah, Country.

\subsection*{Conference posters}
\noindent
\years{2017}\textbf{Name.} Title. Poster presented at Blah Conference, Date \& Year, Place, Country.


\subsection*{Public talks}
\noindent
\years{2017}\textbf{Name.} Title. Talk given at Blah Event, Date \& Year, Organizer, Country. \\


%\hrule
\section*{\faTrophy \thinspace Honors, awards \& scholarships}

\years{2016-2017}Blah Scholarship, University of Blah \\


%\hrule
\section*{\faMoney \thinspace Fundings \& grants}

\subsection*{Internal \& External fundings}
\noindent
\years{2016-2017}Departmental Funding

\subsection*{Travel grants}
\noindent
\years{2015-2017}Faculty Travel Grant, University of Blah \\


%\hrule
\section*{\faCalendarCheckO \thinspace Professional services}

\subsection*{Reviewing}
\noindent
\years{2017-}\emph{Journal}.

\subsection*{Organizing}
\noindent
\years{2016-2017}Organizer, \emph{Event}. Department of Blah, University of Blah \\

\subsection*{Outreach}
\noindent
\years{2017 Spring}Linguistic Consultant for \emph{Event}, Organizer \\


%\hrule
\section*{\faUsers \thinspace Membership}

\years{2017-}Linguistic Society of Blah \\


%\hrule
\section*{\faWrench \thinspace Skills}

\subsection*{Languages}
English: full professional proficiency \\
Spanish and German: elementary level

\subsection*{Computing}
Programming \& Statistics: R, SPSS, JavaScript, Python \\
Experimental: E-Prime, E-Run, Experiment Builder, Eyelink \\




%\vspace{1cm}
\vfill{}
%\hrulefill

\begin{center}
{\scriptsize  Last updated: \today\- •\- }
\end{center}

\end{document}
